Bayesian Reconstruction of Coevolutionary Histories

### 2013-09-15 paper/article.tex
Improved integral notation
Played with diagrams/layout

% Layout and formatting
\usepackage[margin=1in]{geometry}
\usepackage{csquotes}
\usepackage{fixltx2e}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{units}
\frenchspacing

% Bibliography
\usepackage[american]{babel}
\usepackage[backend=biber,style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\bibliography{bibliography.bib}

% Graphics
\usepackage{graphicx}
\usepackage[pdf]{pstricks}
\psset{unit=1in,linewidth=0.02}

@@

% Math
\usepackage{algorithm2e}

\title{BECKY:\\Bayesian Estimation of Coevolutionary KrYteria}

@@

\begin{titlepage}
\null
\vfil
\let\newpage\relax\maketitle
\vfil
\centering
\includegraphics[width=2.5in]{figures/icon.pdf}
\vfil
\end{titlepage}

@@

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0.5)(0.5,0.5)
\psline(0.5,0.3)(1,0.3)
\psline(0.5,0.7)(1,0.7)
\psline(0.5,0.3)(0.5,0.7)
\psline[linestyle=dashed](0,0.6)(0.4,0.6)
\psline[linestyle=dashed](0.4,0.4)(1,0.4)
\psline[linestyle=dashed](0.4,0.8)(1,0.8)
\psline[linestyle=dashed](0.4,0.4)(0.4,0.8)
\end{pspicture}
\caption{cospeciation}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.3)
\psline[linestyle=dashed](0.5,0.3)(1,0.3)
\end{pspicture}
\caption{duplication}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline(0,0.4)(1,0.4)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.5)
\psline[linestyle=dashed](0.5,0.5)(1,0.5)\end{pspicture}
\caption{host-shift}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(0.8,0.1)
\rput(0.8,0.1){\textsf{X}}
\end{pspicture}
\caption{loss}
\end{subfigure}
\caption{Diagrams of the four cophylogenetic events considered in my model, which was coined the four-event model by \textcite{Ronquist:2003}, where the host phylogeny and the symbiont dashed. All events are branch events (i.e., they can occur at any point), except cospeciation, which is a nodal event (and thus can occur only when the host speciates).}
\end{figure}

@@

>>>>

% Layout and formatting
\usepackage[margin=1in]{geometry}
\usepackage{acronym}
\usepackage{csquotes}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{units}
\frenchspacing

% Graphics
\usepackage{graphicx}
\usepackage[pdf]{pstricks}
\psset{unit=1in,linewidth=0.02,arrows=C-C,arrowsize=0.2}

% Bibliography
\usepackage[american]{babel}
\usepackage[backend=biber,style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\bibliography{bibliography.bib}
\usepackage{doi}

@@

% Math
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{mathtools}
\usepackage{commath}

\title{Bayesian Reconstruction of Coevolutionary Histories}

% Acronyms
\acrodef{MCMC}{Markov chain Monte Carlo}
\acrodef{GTR}{general time reversible}

@@

\begin{titlepage}
\null
\vfil
\let\newpage\relax
\maketitle
\vfil
\centering
\begin{pspicture}(16,12)
\psset{unit=0.5cm,linewidth=0.2}
\psline[linecolor=blue](0,0)(10,10)
\psline[linecolor=blue](4,0)(2,2)
\psline[linecolor=blue](8,0)(4,4)
\psline[linecolor=blue](12,0)(14,2)
\psline[linecolor=blue](16,0)(8,8)
\psline[linecolor=red](-1,0)(9,10)
\psline[linecolor=red](15,0)(7,8)
\psline[linecolor=red](11,0)(13,2)
\psline[linecolor=red](4,3)(12,3)
\psline[linecolor=red,arrows=<-](8,3)(12,3)
\psline[linecolor=red](7,0)(4,3)

\end{pspicture}
\vfil
\end{titlepage}

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline[linecolor=blue](0,0.5)(0.5,0.5)
\psline[linecolor=blue](0.5,0.3)(1,0.3)
\psline[linecolor=blue](0.5,0.7)(1,0.7)
\psline[linecolor=blue](0.5,0.3)(0.5,0.7)
\psline[linecolor=red](0.4,0.4)(1,0.4)
\psline[linecolor=red](0.4,0.8)(1,0.8)
\psline[linecolor=red](0.4,0.4)(0.4,0.8)
\psline[linecolor=red,arrows=-o](0,0.6)(0.4,0.6)
\end{pspicture}
\caption{cospeciation}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline[linecolor=blue](0,0)(1,0)
\psline[linecolor=red](0,0.1)(1,0.1)
\psline[linecolor=red,arrows=*-](0.5,0.1)(0.5,0.3)
\psline[linecolor=red](0.5,0.3)(1,0.3)
\end{pspicture}
\caption{duplication}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline[linecolor=blue](0,0)(1,0)
\psline[linecolor=blue](0,0.4)(1,0.4)
\psline[linecolor=red](0,0.1)(1,0.1)
\psline[linecolor=red](0.5,0.1)(0.5,0.5)
\psline[linecolor=red,arrows=->,arrowsize=0.1](0.5,0.1)(0.5,0.35)
\psline[linecolor=red](0.5,0.5)(1,0.5)
\end{pspicture}
\caption{host-shift}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline[linecolor=blue](0,0)(1,0)
\psline[linecolor=red](0,0.1)(0.8,0.1)
\rput(0.8,0.1){\large\textcolor{red}{\textsf{x}}}
\end{pspicture}
\caption{loss}
\end{subfigure}
\caption{Diagrams of the four cophylogenetic events considered in my model, where the host organism's phylogeny is in blue and the symbiont phylogeny in red. All events are branch events (i.e., they can occur at any point along a branch), except cospeciation, which is a nodal event (and thus can occur only when the host speciates).}
\end{figure}

@@

%\begin{equation}
%P\left(M,\Theta_M|D\right) \propto \int\limits_{T_H \times T_S} \overbrace{P\left(d_H|t_H,\theta_H\right)}^{\mathclap{\text{Felsenstein likelihood for host tree}}} \underbrace{P\left(d_S|t_S,\theta_S\right)}_{\mathclap{\text{Felsenstein likelihood for symbiont tree}}} P\left(d_M|M,\theta_M,t_H,t_S\right) P\left(M\right) \textrm{d}T_H \times T_S 
%\end{equation}

%\begin{equation}
%P\left(m,\theta|D\right) \propto \int\limits_{T_\textrm{H} \times T_\textrm{S}}  P\left(d_\textrm{M}|m, \theta\right) P\left(t_\textrm{H}|d_\textrm{H}\right) P\left(t_\textrm{S}|d_\textrm{S}\right) P\left(\theta\right) \textrm{d} t_\textrm{H},t_\textrm{S} 
%\end{equation}
%
%This integral can be approximated via a \ac{MCMC} analysis.
%
%Nevertheless, it is possible to model these events on the principle of observation; i.e., what specific event or events are we observing.
%
%For example, we can consider molecular evolution.

@@

%The effects of the cophylogenetic likelihood on mixing of the MCMC chain needs to be seriously investigated.
